**{shorts}**: An R Package for Modeling Short Sprints

### 2022-07-21 shorts-paper.Rmd
Removed visible chunk of code that shouldn't be there

Here is an example using a built-in dataset. We are going to filter out one athlete (e.g., John) with the help of the **tidyverse** [@R-tidyverse] package and estimate MSS, TAU, and MAC parameters using the `model_timing_gates()` function:

@@

To create a simple plot of the model, use the S3 `plot()` method, which returns **ggplot2** [@R-ggplot2] object:

@@

Plotting the model predictions can be done once we convert data from wide to long with the help of **ggplot2** [@R-ggplot2], **dplyr** [@R-dplyr], and **tidyr** [@R-tidyr] packages (loaded already using the **tidyverse** [@R-tidyverse] package):

@@

### How to overcome missing the initial force production when using timing gates?

@@

```{r}
# Residuals
ggplot(
  model_df,
  aes(
    y = residuals,
    x = distance,
    color = flying_start_distance,
    group = flying_start_distance
  )
) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  facet_wrap(~model) +
  xlab("Distance (m)") +
  ylab("Observed - predicted time (s)") +
  theme(legend.position = "top") +
  labs(color = "Flying start distance")
```

>>>>

Here is an example using a built-in dataset. We are going to filter out one athlete (e.g., John) with the help of the **{tidyverse}** [@R-tidyverse] package and estimate MSS, TAU, and MAC parameters using the `model_timing_gates()` function:

@@

To create a simple plot of the model, use the S3 `plot()` method, which returns **{ggplot2}** [@R-ggplot2] object:

@@

Plotting the model predictions can be done once we convert data from wide to long with the help of **{ggplot2}** [@R-ggplot2], **{dplyr}** [@R-dplyr], and **{tidyr}** [@R-tidyr] packages (loaded already using the **{tidyverse}** [@R-tidyverse] package):

@@

## How to overcome missing the initial force production when using timing gates?

@@

```{r echo=FALSE}
# Residuals
ggplot(
  model_df,
  aes(
    y = residuals,
    x = distance,
    color = flying_start_distance,
    group = flying_start_distance
  )
) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  facet_wrap(~model) +
  xlab("Distance (m)") +
  ylab("Observed - predicted time (s)") +
  theme(legend.position = "top") +
  labs(color = "Flying start distance")
```
